%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Experience}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {Cascadia Technical Mentorship} % Organization
    {Winlock, USA} % Location
    {Jan. 2016 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with various international corporate and nonprofit clients to improve their information management, security and duty of care.}
        \item {Helped staff and managers foster vibrant security cultures in their organizations based on sound policies and tools.}
        \item {Assisted clients in porting legacy geospatial infrastructure from Python and Ruby to Go.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Volunteer Build Coach} % Job title
    {Free Geek} % Organization
    {Portland, USA} % Location
    {Feb. 2015 - Dec 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped Spanish speaking immigrants improve their technical skills and employment prospects through the computer rebuild program.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Regional Security Manager} % Job title
    {Greenpeace Southeast Asia} % Organization
    {Jakarta, Indonesia} % Location
    {Jan. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with research and logistics teams to manage the safety and security of their operations in remote and conflict-prone locations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Campaigner} % Job title
    {The Wilderness Society Australia} % Organization
    {Sydney, Australia} % Location
    {Dec. 2010 - Aug. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with diverse stakeholders to develop a data-driven strategic plan for river conservation leading to enhanced environmental outcomes.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Logistician, Field Coordinator, Logistics Manager, Board Member} % Job title
    {Médecins Sans Frontières (Doctors Without Borders)} % Organization
    {Various} % Location
    {Jan. 2002 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed to Somalia, Afghanistan, Tanzania, Sri Lanka, Malawi and Papua New Guinea.}
        \item {Worked with teams of medical and logistics professionals to bring immediate relief to populations affected by natural disasters and conflict.}
        \item {Participated in global governance reform as a member of the board of directors of the Australian branch.}
       \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {International Actions and Logistics Manager} % Job title
    {Greenpeace International} % Organization
    {Amsterdam, The Netherlands} % Location
    {May 2007 - Nov. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported the ability of national actions and logistics teams to deliver their work through coaching, mentoring and technical advice.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Officer} % Job title
    {Department of Natural Resources, Queensland Government} % Organization
    {Brisbane, Australia} % Location
    {Feb 1997 - Jan. 2000} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped research teams communicate their work through various mediums, including scientific publishing, printed and online maps.}
      \end{cvitems}
    }


%---------------------------------------------------------

\end{cventries}
